---
title: "Locational analysis of chain hotels in Japanese urban city"
author:
- name: Keigo Matsuo
  affiliation:  
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    md_extensions: -ascii_identifiers
---
<style type="text/css">

body{ /* Normal  */
      font-size: 18px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  margin-top : 50px ;
  margin-bottom : 70px ;
  font-size: 28px;
  color: DarkRed;
}

h1 { /* Header 1 */
  font-size: 18px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 18px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 18px;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>
----------------------------------------------------------------------    
    
    
    
    
    
#1.Introduction
The study of hotel location facilitates the understanding of urban tourism space and structure because hotels are the basic facilities that support urban tourism(Rogerson,2012a)[^1] and their locations influence tourists' movement within a city(Shoval et al.,2011)[^2].

#2.Literature review

#3.Data and Method

#4.Analysis
##4.1 rooms
```{r include=FALSE,echo=FALSE}
##packages
library(fancycut)
library(ggplot2)
library(gridExtra)
library(ggrepel)
library(ggthemes)
library(xtable) 
library(dplyr)
```

```{r message=FALSE, warning=FALSE, error=FALSE,fig.width=7, fig.height=6,fig.align='center'}
#retrive chain hotel data
osaka <- read.csv("https://raw.githubusercontent.com/kmbsweb/hotel-location/master/chosaka.csv")
tokyo <- read.csv("https://raw.githubusercontent.com/kmbsweb/hotel-location/master/chtokyo.csv")

#and then...
#create index of transit level
osaka$index <- (log(osaka$kanku_dura)+log(osaka$itami_dura))
tokyo$index <- (log(tokyo$narita_dur)+log(tokyo$haneda_dur))

osaka$roomsclass <- fancycut(x = osaka$rooms,
                             intervals = c("[0,128.5)", "[128.5,202.5)",
                                           "[202.5,318.8)","[318.8, 972.0]"),
                             buckets = c("under 128.5", "128.5-202.5",
                                         "202.5-318.8","more than 318.8"),
                             unmatched.bucket = "範囲外")

#plot
ggplot()+
  geom_point(data=osaka, aes(x=log(lvalue), y=index)) + 
  geom_vline(xintercept=mean(log(osaka$lvalue)),
             linetype=2,colour = "gray")+
  geom_hline(yintercept=mean(osaka$index),
             linetype=2,colour = "gray")+
  stat_density2d(aes(x =log(lvalue), y = index, fill = ..level.., alpha = ..level..),
                 bins = 10, geom = "polygon",data=osaka) +
  scale_fill_gradient(low = "black", high = "red") +
  facet_wrap(~ roomsclass) +
  labs(title="difference of rooms in Osaka", x="ln(land value)", y="ln(accessibility index)") +
  theme_classic()
```

```{r message=FALSE, warning=FALSE, error=FALSE,fig.width=7, fig.height=6,fig.align='center'}
summary(tokyo$rooms)
tokyo$roomsclass <- fancycut(x = tokyo$rooms,
                             intervals = c("[0,105.0)", "[105.0,156.0)","[156.0,238.0)","[238.0, 3560.0]"),
                             buckets = c("under 105.0", "105.0-156.0", "156.0-238.0","more than 238.0"),
                             unmatched.bucket = "except")
library(ggplot2)
ggplot()+
  geom_point(data=tokyo, aes(x=log(lvalue), y=index)) + 
  geom_vline(xintercept=mean(log(tokyo$lvalue)),
             linetype=2,colour = "gray")+
  geom_hline(yintercept=mean(tokyo$index),
             linetype=2,colour = "gray")+
  stat_density2d(aes(x =log(lvalue), y = index, fill = ..level.., alpha = ..level..),
                 bins = 10, geom = "polygon",data=tokyo) +
  scale_fill_gradient(low = "black", high = "red") +
  facet_wrap(~ roomsclass) +
  labs(title="difference of rooms in Tokyo", x="ln(land value)", y="ln(accessibility index)") +
  theme_classic()
```

##4.2 open year
```{r message=FALSE, warning=FALSE, error=FALSE,fig.width=7, fig.height=4.5,fig.align='center'}
summary(osaka$o_year)
osaka$yearclass <- fancycut(x = osaka$o_year,
                             intervals = c("[0,2003)", "[2003,2013)", "[2013, 2017]"),
                             buckets = c("before 2003", "2003-2013", "afrer 2017"),
                             unmatched.bucket = "except")

ggplot()+
  geom_point(data=osaka, aes(x=log(lvalue), y=index)) + 
  geom_vline(xintercept=mean(log(osaka$lvalue)),
             linetype=2,colour = "gray")+
  geom_hline(yintercept=mean(osaka$index),
             linetype=2,colour = "gray")+
  stat_density2d(aes(x =log(lvalue), y = index, fill = ..level.., alpha = ..level..),
                 bins = 8, geom = "polygon",data=osaka) +
  scale_fill_gradient(low = "black", high = "red") +
  facet_wrap(~ yearclass) +
  labs(title="difference of open year in Osaka", x="ln(land value)", y="ln(accessibility index)") +
  theme_classic()
```

```{r message=FALSE, warning=FALSE, error=FALSE,fig.width=7, fig.height=4.5,fig.align='center'}
summary(tokyo$o_year)
tokyo$yearclass <- fancycut(x = tokyo$o_year,
                            intervals = c("[0,2003)", "[2003,2013)", "[2013, 2017]"),
                            buckets = c("before 2003", "2003-2013", "afrer 2017"),
                            unmatched.bucket = "except")

ggplot()+
  geom_point(data=tokyo, aes(x=log(lvalue), y=index)) + 
  geom_vline(xintercept=mean(log(tokyo$lvalue)),
             linetype=2,colour = "gray")+
  geom_hline(yintercept=mean(tokyo$index),
             linetype=2,colour = "gray")+
  stat_density2d(aes(x =log(lvalue), y = index, fill = ..level.., alpha = ..level..),
                 bins = 8, geom = "polygon",data=tokyo) +
  scale_fill_gradient(low = "black", high = "red") +
  facet_wrap(~ yearclass) +
  labs(title="difference of open year in Tokyo", x="ln(land value)", y="ln(accessibility index)") +
  theme_classic()
```

##4.3 experienced
```{r message=FALSE, warning=FALSE, error=FALSE,fig.width=6, fig.height=4,fig.align='center'}
#retrive experiemced data
osakaE <- read.csv("https://raw.githubusercontent.com/kmbsweb/hotel-location/master/osaka_expand.csv")
tokyoE <- read.csv("https://raw.githubusercontent.com/kmbsweb/hotel-location/master/tokyo_expand.csv")

osakaE$exclass <- fancycut(x = osakaE$expantion,
                            intervals = c("[0,5)", "[5, 22]"),
                            buckets = c("few experiemced", "experienced"),
                            unmatched.bucket = "except")
tokyoE$exclass <- fancycut(x = tokyoE$expantion,
                           intervals = c("[0,5)", "[5, 52]"),
                           buckets = c("few experiemced", "experienced"),
                           unmatched.bucket = "except")

osaka <- left_join(osaka,osakaE,by="brand")
tokyo <- left_join(tokyo,tokyoE,by="brand")

###########################
#osaka#####################
###########################
ggplot()+
  geom_point(data=osaka, aes(x=log(lvalue), y=index)) + 
  geom_vline(xintercept=mean(log(osaka$lvalue)),
             linetype=2,colour = "gray")+
  geom_hline(yintercept=mean(osaka$index),
             linetype=2,colour = "gray")+
  stat_density2d(aes(x =log(lvalue), y = index, fill = ..level.., alpha = ..level..),
                 bins = 8, geom = "polygon",data=osaka) +
  scale_fill_gradient(low = "black", high = "red") +
  facet_wrap(~ exclass) +
  labs(title="difference of expereiced in Osaka", x="ln(land value)", y="ln(accessibility index)") +
  theme_classic()
```

```{r message=FALSE, warning=FALSE, error=FALSE,fig.width=6, fig.height=4,fig.align='center'}
###########################
#tokyo#####################
###########################
ggplot()+
  geom_point(data=tokyo, aes(x=log(lvalue), y=index)) + 
  geom_vline(xintercept=mean(log(tokyo$lvalue)),
             linetype=2,colour = "gray")+
  geom_hline(yintercept=mean(tokyo$index),
             linetype=2,colour = "gray")+
  stat_density2d(aes(x =log(lvalue), y = index, fill = ..level.., alpha = ..level..),
                 bins = 8, geom = "polygon",data=tokyo) +
  scale_fill_gradient(low = "black", high = "red") +
  facet_wrap(~ exclass) +
  labs(title="difference of expereiced in Tokyo", x="ln(land value)", y="ln(accessibility index)") +
  theme_classic()
```


##4.4 table
```{r message=FALSE, warning=FALSE, error=FALSE}
library(knitr)
library(kableExtra)
dt <-data.frame(variables =c(rep("rooms", 4),rep("open year", 2)),classification =c("too many","many","little","few","before 2013","after 2013"), I=c("","","","","",""),II=c("","","","","",""), III=c("","","","","",""),IV =c("","","◎","","",""))
# HTML table
kable(dt, format = "html", caption = "Evaluate Table", booktabs = T, align = "c") %>%
  kable_styling(full_width = T)  %>%
  add_header_above(c(" ", " ","Osaka" = 4)) %>%
  collapse_rows(columns = 1)
```

```{r message=FALSE, warning=FALSE, error=FALSE}
dt <-data.frame(variables =c(rep("rooms", 4),rep("open year", 2)),classification =c("too many","many","little","few","before 2013","after 2013"), I=c("","","","","",""),II=c("","","","","",""), III=c("","","","","",""),IV =c("","","◎","","",""))
# HTML table
kable(dt, format = "html", caption = "Evaluate Table", booktabs = T, align = "c") %>%
  kable_styling(full_width = T)  %>%
  add_header_above(c(" ", " ","Tokyo" = 4)) %>%
  collapse_rows(columns = 1)
```

#5.Discussion

#6.Conclusion

# Reference
[^1]: Rogrerson,J.M.,2012a.The changing location of hotels in South Africa's coastal cities,1990-2010.Urban Forum23(1),73-91.
[^2]: Shoval, N., McKercher, B., Ng, E., Birenboim, A., 2011. Hotel location and tourist activity in cities. Annals of Tourism Research 38 (4), 1594–1612.
